ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-05-06 paper.tex
Fixed table@

\begin{table}
  \centering
  \caption{A summary of the results. }\label{tab:results}
  \begin{tabular}{ccccc}
    \toprule
     & avg & std & avg &std \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}
  \centering
  \caption{A summary of the results. }\label{tab:results}
  \begin{tabular}{p{5cm}p{2cm}p{2cm}}
    \toprule
    & \textbf{Guided} & \textbf{Unguided} \\\midrule
    TAR [\%]           & $46\pm13$ & $54\pm15$   \\\midrule
    Time to target [s] & $12.5\pm11.9$ & $17.2\pm11.5$ \\\midrule
    Pan Angle Displacement [rad] & $0.68\pm1.1$ & $0.99\pm1.2$ \\\midrule
    Tilt Angle Displacement [rad] & $0.68\pm1.1$ & $1.04\pm1.2$ \\\midrule
    Linear Displacement [rad] & $0.23\pm0.22$ & $0.36\pm0.22$ \\\midrule
    \bottomrule
  \end{tabular}
\end{table}
